---
title: "COVID-19 Spatial Analysis"
author: "Izzy Youngs"
date: "5/7/2020"
output: 
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(here)
```

## Analysis goal and data requirements
To illuminate which factors and variables drive the biggest differences in community spread of coronavirus, I turned to Random Forest Regression, a supervised learning technique which combines the result of multiple forest regressions and then aggregates them, making it more powerful than any single forest regression, which tend to overfit the data. 

This spatial statistics tool is very powerful and can be fine-tuned to improve the quality of the model's prediction confidence. Random Forest Regressions attempt to predict the value of a single variable (in this example, the case ratio) based on the values of other variables selected.

Based on various reports about the potential transmission factors, I isolated the following variables for analysis:

```{r data, echo=FALSE, include = FALSE}
requirements_table <- read_csv("~/GitHub/covid-19/Data/analysis_table.csv")
```

```{r requirements, echo=FALSE}
kable(requirements_table)
```

## Step-by-step documentation

Step-by-step documentation of your analysis steps, to include relevant tools used


## Storymap
A link to a completed Story Map app that walks users through your analysis and presents the results

```{r pressure, echo=FALSE}
plot(pressure)
```